(Deep) Induction for GADTs

### 2021-04-13 induction-paper/ENTCS-GADT-induction.tex
revising Sections 1-4

  \,(List^{\wedge}\, A\, Q)\, (List^{\wedge}\, A\, Q')}$ {\color{red}
  defined by ?????} takes a morphism $\mathsf{f}$ of predicates and
produces a morphism of lifted predicates {\color{red} by mapping
  $\mathsf{f}$ over the input list to which $\mathsf{Q}$ is lifted ---
  or other simple description?}

>>>>

  \,(List^{\wedge}\, A\, Q)\, (List^{\wedge}\, A\, Q')}$, which takes
a morphism $\mathsf{f}$ of predicates and produces a morphism of
lifted predicates, is defined by $\mathsf{liftListMap\, A\, Q\, Q'\,
  m\, nil\, tt = tt}$ (since $\mathsf{x : List^{\wedge}\, A\, Q\, nil
  = \top}$ must necessarily be $\mathsf{tt}$), and by
$\mathsf{liftListMap\, A\, Q\, Q'\, m\, (cons\, a\, l')\, (y, x') =
  (m\,a\,y, liftListMap\, A\, Q\, Q'\, m\, l'\, x')}$ since $\mathsf{x
  : List^{\wedge}\, A\, Q\, (cons\, a\, l') = \top}$ must be of the
form $\mathsf{x = (y, x')}$ where $\mathsf{y : Q\,a}$ and $\mathsf{x'
  : List^{\wedge}\, A\, Q\, l'}$. {\color{red} Double-check the
  previous paragraph.}
